Ground state energy of quantum dots using the coupled cluster method

### 2018-06-04 project_2/article/article.tex
Update rewritten amplitude equation

		The we can define a new function consisting of all of \autoref{eq:CCD_amp_1} 
		except term number two and three,
		\begin{equation}
		\begin{aligned}		
			g(u, \tau) =&
					u^{ab}_{ij} + \tilde{f}^b_c t^{ac}_{ij}P(ab) - \tilde{f}^k_jt^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}, 
		\end{aligned}
		\end{equation}

@@

		Now we have $D_{ij}^{ab}t_{ij}^{ab} = g(u, \tau)$. 
		This allows us to define an iterative scheme,
		\begin{equation}
			\tau^{(k + 1)} = \frac{g(u, \tau^{(k)})}{D_{ij}^{ab}},
		\end{equation}
		with the initial guess
		\begin{equation}
			\tau^{(0)} = \frac{u_{ij}^{ab}}{D_{ij}^{ab}}.
		\end{equation}

		\subsubsection{Intermediate Computations}
		Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
		to realize that it contains that this equation contains many of the same structures in
		several of the terms. This warrants the search for an algebraic transformation of the
		CCD amplitude equation that has the potential to reduce the amount of floating point
		operations needed to compute it. As it turns out, such terms exist and they will decrease
		the computing time necessary by an order of magnitude. We will define the following
		"intermediates",
		\begin{align}
			 \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
    			 \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
   			 \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} \\
    			 \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd}.
		\end{align}
		These intermediate structures will allow us to rewrite \autoref{eq:CCD_amp_1} to,
		THIS REMAINS TO BE CHECKED!! 
		\begin{equation}
		\begin{aligned}
			0 =& \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij} - t^{ab}_{im}u^{mn}_{jn}P(ij)
      		+ t^{cd}_{ij}\chi^{ab}_{cd} - t^{bd}_{ij}\chi^a_d P(ab) \\
      	  &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
      		+ t^{ab}_{in}\chi^n_jP(ij) + u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
		The importance of this "trick" will become apparent in due time.

>>>>

            The we can define a new function consisting of all of \autoref{eq:CCD_amp_1}
            except term number two and three,
            \begin{equation}
            \begin{aligned}
                g(u, t) =&
                        u^{ab}_{ij} + \tilde{f}^b_c t^{ac}_{ij}P(ab) - \tilde{f}^k_jt^{ab}_{ik}P(ij) \\
                     +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
                     +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
                     +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
                     +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij},
            \end{aligned}
            \end{equation}

@@

            Now we have $D_{ij}^{ab}t_{ij}^{ab} = g(u, t)$.
            This allows us to define an iterative scheme,
            \begin{equation}
                t^{(k + 1)} = \frac{g(u, t^{(k)})}{D_{ij}^{ab}},
            \end{equation}
            with the initial guess
            \begin{equation}
                t^{(0)} = \frac{u_{ij}^{ab}}{D_{ij}^{ab}}.
            \end{equation}

        \subsubsection{Intermediate Computations}
            Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
            to realize that it contains that this equation contains many of the same structures in
            several of the terms. This warrants the search for an algebraic transformation of the
            CCD amplitude equation that has the potential to reduce the amount of floating point
            operations needed to compute it. As it turns out, such terms exist and they will decrease
            the computing time necessary by an order of magnitude. We will define the following
            "intermediates",
            \begin{align}
                 \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
                     \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
                    \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} \\
                     \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd}.
            \end{align}
            These intermediate structures will allow us to rewrite
            \autoref{eq:CCD_amp_1} to
            \begin{align}
                0 &=
                u^{ab}_{ij} + \tilde{f}^b_c t^{ac}_{ij}P(ab)
                - \tilde{f}^k_jt^{ab}_{ik}P(ij)
                \nonumber\\
                &\qquad
                + t^{cd}_{ij}\chi^{ab}_{cd}
                + t^{ab}_{in}\chi^n_jP(ij)
                - t^{bd}_{ij}\chi^a_d P(ab)
                \nonumber\\
                &\qquad
                + t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
                + \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij}.
            \end{align}
            The importance of this "trick" will become apparent in due time.
